---
title: "tableHTML"
subtitle: "Budapest-BI"
author: "Theo Boutaris, Clemens Zauchner, Dana Jomar"
date: "14 November 2019"
output: 
  ioslides_presentation:
    df_print: null
    theme: null
    css: style.css
    logo: img/tableHTML.png
    widescreen: true
    keep_md: true
    #smaller: true  ## only works without "---" slide breaks (use ##)
    slide_level: 2
#search and replace:
# !\[\]\((.*)\)
# 
# ```{r, eval = TRUE, echo = FALSE, out.width = "100%", fig.align = "left"}
# knitr::include_graphics("\1")
# ```
# 
# OLD:  
# ```{r, eval = TRUE, echo = FALSE}
# grid::grid.raster(png::readPNG("\1"))
# ```
# use {.smaller} after title for single slides

    # 'f' enable fullscreen mode
    # 'w' toggle widescreen mode
    # 'o' enable overview mode
    # 'h' enable code highlight mode
    # 'p' show presenter notes
#
# two-column layout:
#   ## title {.columns-2}
#  or:
#   <div class="columns-2">  </div>
#  or:
#   <div style="float: left; width: 50%;"> </div>  ## awesome! might need a <div> </div> before the columns... (only "left" also works)
#   <div></div> <div style="float: left; width: 50%;"> </div> <div style="float: left; width: 50%;"> </div> 
# color:
#   <div class="red2"></div>
#   <font color="red">
#
# slide layout: after title, place:
#   {.flexbox .vcenter}
#   { .smaller}
#   
---
[//]: # (
http://www.w3schools.com/css/css_font.asp
http://www.cssfontstack.com/Helvetica
)

<style>
/* gdbar size (that contains logo) on title page */
/* needs to have greater height than logo image, other stuff is irrelevant */
.gdbar {
  position:absolute !important;
  top: 50px !important; left: auto; right: 0px !important; width: 0px !important;
  height: 500px !important;  /* modify if logo is larger than this in height */
}
/* logo size on title page */
.gdbar img {
  position: absolute; 
  top: 0px;
  left: 110px;
  width:  248px !important;
  height: 275px !important;
}
/*77 64*/
/* logo size on slides */
slides > slide:not(.nobackground):before {
  width: 120px; height: 130px; /* modify width and height (twice) */
  background-size: 124px 137.5px;
  position: absolute; left: auto;
  right: -30px;  /* modify position */
  top: 10px;
}
/* for slides with red background (only works for normal text, not whole slide) {.bgred} */
.bgred,
.bgred div,
.bgred body,
.bgred .article,
.bgred article,
.bgred .prettyprint,
.bgred .h1,
.bgred .h2,
.bgred .h3,
.bgred backdrop,
.bgred .backdrop,
.bgred .slide,
.bgred slide,
.bgred slides > slide.backdrop {   
  background-color:#ffaaaa;
  background:#ffaaaa;
}
.footer {
    position: fixed;
    top: 70%;
    width:100%;
}
/*slides > slide.backdrop {   */
/*  background-color:#ffaaaa;   */
/*  background:#ffaaaa;   */
/*}   */
</style>

## Contents

- Introduction
- Basic Options
- Themes
- Add CSS customizations
- Shiny


```{r child = 'Introduction.Rmd'}
```

```{r child = 'Basic_options.Rmd'}
```

```{r child = 'Themes.Rmd'}
```

```{r child = 'Add_css.Rmd'}
```

```{r child = 'Shiny.Rmd'}
```

# Thank You
<div style="color: white;">
- If you need help using the package, there is a `tableHTML` tag on stackoverflow:
<br>https://stackoverflow.com/questions/tagged/tablehtml

- If you find any bugs please report them on the issues page on github.
<br>https://github.com/LyzandeR/tableHTML/issues
</div>
